### 2020-05-08 README.Rmd
small change to readme

System        | .Renviron file locations
--------------|-------------------------
MS Windows    | `C:\Users\<username>\.Renviron`  or `C:\Users\<username>\Documents\.Renviron`
Linux / MacOs | `/home/<username>/.Renviron`

>>>>

System        | .Renviron file locations
--------------|-------------------------
MS Windows    | <code>C:\Users\&lt;username&gt;\.Renviron</code>  or <code>C:\Users\&lt;username&gt;\Documents\.Renviron</code>
Linux / MacOs | <code>/home/&lt;username&gt;/.Renviron</code>
